---
title: "Tutorial"
output: learnr::tutorial
runtime: shiny_prerendered
---

```{r setup, include=FALSE}
library(learnr)
knitr::opts_chunk$set(echo = FALSE)
```


## Welcome to Turtle Town

### Exercise: Load package

*If we're going to turtle town, we have to load the `TurtleGraphics` package for `R`. We do that by running `library(TurtleGraphics)`.*

This runs automatically:

```{r load-lib}
library(TurtleGraphics)
```


### Exercise with Code

Now initialize the turtle by running the following code chunk:

```{r add-function, exercise=TRUE}
turtle_init()
```

### Move the Turtle

We can move the turtle by giving it commands. Alter the distance parameter below and see what happens:

```{r print-limit, exercise=TRUE, exercise.eval=TRUE}
turtle_init()

turtle_forward(dist=30)
```

```{r print-limit-hint}
head(mtcars)
```

### Quiz

*You can include any number of single or multiple choice questions as a quiz. Use the `question` function to define a question and the `quiz` function for grouping multiple questions together.*

Some questions to verify that you understand the purposes of various base and recommended R packages:

```{r quiz}
quiz(
  question("Which package contains functions for installing other R packages?",
    answer("base"),
    answer("tools"),
    answer("utils", correct = TRUE),
    answer("codetools")
  ),
  question("Which of the R packages listed below are used to create plots?",
    answer("lattice", correct = TRUE),
    answer("tools"),
    answer("stats"),
    answer("grid", correct = TRUE)
  )
)
```

